---
title: "Week 11_Helee"
author: "Helee Rana"
date: "5/4/2020"
output:
  word_document: default
  html_document: default
---

## Prediction about the customer will continue the Phone service with the company or not
```{r}
require(tidyverse)

churn=read.csv("/Users/heleerana/Desktop/DATA MINING Prof. YEGIN/WA_Fn-UseC_-Telco-Customer-Churn.csv")
head(churn)

```

## Since Senior citizen columnis in 0s and 1s (integer), we will need to convert to character
```{r}
churn=churn%>%mutate(SeniorCitizen=as.character(SeniorCitizen))

## We dont require customer id

churn=churn%>%select(-customerID)

```

## Now we have tenure and other 3 columns as integer value, to implement naive bayes, the integer values in a column should be normally distributed. So lets check whether tenure other 3 columns are normally distributed or not
```{r}
hist(churn$tenure) ## Candidate for binning
## We can see that the graph is not normally distributed
## Now two options are to ignore the tenure column OR binning

hist(churn$MonthlyCharges) ## Candidate for binning
## Same for MonthlyCharges

hist(churn$TotalCharges)
## The graph seems exponential, Therefore now we take square root of the values
hist(sqrt(churn$TotalCharges)) ## sqrt transformation
```
```{r}
## Binning, that means dividing the values into two
 ## one method 
##cbind(churn$tenure, as.factor(cut(churn$tenure, 2)))

## second method if we  want to insert labels as low and high
##churn%>%mutate(tenure=cut(tenure,2, labels=c('low', 'high')))

## Now we apply the second method to tenure, monthlycharges
churn2=churn%>%mutate(tenure=cut(tenure,2), MonthlyCharges=cut(MonthlyCharges, 4), TotalCharges=sqrt(TotalCharges))
```


## Model Building and evaluation
```{r}
set.seed(1234)
n=nrow(churn2)
training=runif(n)>.3
training_data=churn2[training,]
testing_data=churn2[!training,]

library(e1071)
require(caret)

nb_model=naiveBayes(training_data[-20], as.factor(training_data$Churn))
```

## prediction
```{r}
predictions=predict(nb_model, testing_data[-20], laplace=.1)
```


## Confusion Matrix
```{r}
confusionMatrix(as.factor(predictions), as.factor(testing_data$Churn))
```



